---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# omekasr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-universe version](https://giocomai.r-universe.dev/omekasr/badges/version)](https://giocomai.r-universe.dev/omekasr)
<!-- badges: end -->

The goal of `omekasr` is to facilitate interaction with the Omeka S REST API. 

It is currently only minimally functional. Features are documented in this document as they are introduced and tested.

Planned features include:

- producing pdf reports of Omeka S items

## Installation

You can install the development version of `omekasr` from its main repository on Codeberg:

``` r
remotes::install_git("https://codeberg.org/giocomai/omekasr")
```

or from r-universe with:

``` r
install.packages("omekasr", repos = c("https://giocomai.r-universe.dev", "https://cloud.r-project.org"))
```

## Introducing `omekasr`

The first thing you do when working with `omekasr` is to set the url of the Omeka S instance you want to work with. Throughout the documentation, a dedicated testing instance will be used for reference; its contents are derived from [Omeka S official sandbox instance](https://dev.omeka.org/omeka-s-sandbox/).

```{r o_set}
library("omekasr")
o_set(base_url = "https://omekasr.giorgiocomai.eu/")
```

Internally, this will check that the given input is a valid URL, and will append `api` as requested by Omeka S. 

```{r current_base_url}
current_base_url <- o_set() |> 
  purrr::pluck("base_url")

current_base_url
```

